A Two-Infall Star Formation History with Outflows and Radial Migration

### 2024-05-16 src/tex/ms.tex
remove showyourwork dependency
Add bibfile

\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
% \usepackage{layouts}
\usepackage{xcolor}
% \usepackage{upgreek}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{xspace}

@@

\software{\vice \citep{JohnsonWeinberg2020-Starbursts}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}

@@

\bibliography{bib}

>>>>

% \usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
% \usepackage{layouts}
\usepackage{xcolor}
% \usepackage{upgreek}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{xspace}

@@

\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}

@@

\bibliography{references}
